Generating Simulated Data

### 2021-04-01 docs/SimData.Rmd
update growth file output

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))

@@

  growthpars <- left_join(svexp3, vbout.2) %>%
    mutate(growthType = 4) # use only vonB for now, can change later

>>>>

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))
}

  # read saved sample from above
  survs <- list.files(path=d.name, pattern = "agelensamp.rds", full.names = TRUE)

  survname <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s","*agelensamp.rds"))[,2]

  agelensamp_data <- lapply(survs, readRDS)

  names(agelensamp_data) <- survname

for(s in names(agelensamp_data)){

@@

  growthpars <- left_join(svexp3, vbout.2) %>%
    mutate(growthType = case_when(
      is.na(Linf) ~ 2,
      TRUE ~ 4)) # vonB default, exponential if no vonB
